---
title: "Exploratory analysis of crab OA response"
author: ""
output: 
  html_document:
    css: kable.css
self_contained: yes
runtime: shiny
---

```{r, message = F, warning = F, echo = FALSE}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, dev.args = list(bg = 'transparent', family = 'serif'), eval = T, echo = F)

library(tidyverse)
library(glmulti)
library(MuMIn)
library(gridExtra)
library(Hmisc)
library(grid)
library(scales)
library(kableExtra)
library(ggord)
library(patchwork)
library(shinyWidgets)

source('R/funcs.R')

data(crbs)
data(dissdat)
data(lengdat)
data(envdatdelt)

# get all values and only ph delt
envdatdelt <- envdatdelt %>% 
  filter(!var %in% 'DIC') %>% 
  gather('envtyp', 'envval', val, delt) %>% 
  unite('var', var, envtyp, sep = '') %>% 
  filter(grepl('val$|^pHdelt$', var)) %>% 
  mutate(var = gsub('\\val$', '', var)) %>% 
  rename(val = envval) %>% 
  spread(var, val)

# exp vars to use in cor eval
vars <- c('pH', 'pHdelt', 'Temperature', 'Oxygen', 'Fluorescence')
```

```{r}
column(12, 
  column(4, 
    pickerInput(inputId = "crvrs", label = 'Select variables:', choices = vars,
      options = list(`actions-box` = TRUE, size = 20), selected = vars, multiple = TRUE)    
  ),
  column(4,
    selectInput(inputId = 'dep1', label = 'Select depth:', choices = seq(10, 200, by = 10), selected = 50)
  ), 
  column(4, NULL)
)
column(12, 
  column(4, 
    selectInput('lng', 'Select length measure:', choices = unique(lengdat$lenvar))
  ),
  column(4, 
    selectInput('dssloc', 'Select dissolution location:', choices = unique(dissdat$prt))
  ),
  column(4, 
      selectInput('logm', 'Log models (abundance only):', choices = c(TRUE, FALSE))
)
)
```

```{r}
# all crab bio data with selected dissolution, length measures
crbs_eval <- reactive({
  
  # inputs
  lng <- input$lng
  dssloc <- input$dssloc
  
  # crbs, select only abundance, p/a
  crbs <- crbs %>% 
    select(CTD, abundances, pa)
  
  # filter length and dissolution data
  lengdatsel <- lengdat %>% 
    filter(lenvar %in% lng) %>% 
    select(CTD, avelen) %>% 
    rename(length = avelen)
  dissdatsel <- dissdat %>% 
    filter(prt %in% dssloc) %>% 
    select(CTD, disval) %>% 
    rename(dissolution = disval)
  
  out <- crbs %>% 
    left_join(lengdatsel, by = 'CTD') %>% 
    left_join(dissdatsel, by = 'CTD')

  return(out)
  
})

# data prep, nested for mods
tocor <- reactive({
  
  # input
  dep1 <- as.numeric(input$dep1)
  crvrs <- input$crvrs
  crbs_eval <- crbs_eval()
  logm <- input$logm
  
  out <- envdatdelt %>% 
    filter(depth %in% c(dep1)) %>% 
    left_join(crbs_eval, ., by = 'CTD') %>% 
    dplyr::select_(.dots = c('depth', 'abundances', 'length', 'dissolution', crvrs)) 
  
  if(as.logical(logm))
    out <- out %>%
      mutate(abundances = log10(1 + abundances))
  
  return(out)
  
})

dep1cor <- reactive({
  
  # input
  dep1 <- as.numeric(input$dep1)
  crvrs <- input$crvrs
  tocor <- tocor()
  
  levs <- c(sort(crvrs), sort(c('abundances', 'length', 'dissolution')))
  labs <- levs
  
  dep1cor <- tocor %>% 
    filter(depth == dep1) %>% 
    select(-depth)
  
  dep1cor <- dep1cor[, rev(levs)]
  
  return(dep1cor)
  
})

# all correlations
corplo1 <- reactive({

  # input
  dep1cor <- dep1cor()
  crvrs <- input$crvrs

  levs <- c(sort(crvrs), sort(c('abundances', 'length', 'dissolution')))
  labs <- levs

  crs <- crossing(var1 = names(dep1cor), var2 = names(dep1cor)) %>%
    filter(var1 != var2) %>%
    rownames_to_column() %>%
    group_by(rowname) %>%
    nest %>%
    mutate(
      crs = map(data, function(x){

        # variables
        vr1 <- dep1cor[[x$var1]]
        vr2 <- dep1cor[[x$var2]]

        # pearson
        pr_ts <- cor.test(vr1, vr2, method = 'pearson')
        pr_cr <- round(pr_ts$estimate, 2)
        pr_pv <- p_ast(pr_ts$p.value)
        pr <- paste(pr_cr, pr_pv)

        out <- data.frame(pr = pr, stringsAsFactors = F)
        return(out)

      })
    ) %>%
    unnest %>%
    select(-rowname)
  prplo <- crs %>%
    separate(pr, c('cor', 'sig'), sep = ' ') %>%
    filter(var1 %in% levs & var2 %in% levs) %>%
    mutate(
      cor = as.numeric(cor),
      var1 = factor(var1, levels = rev(levs), labels = rev(labs)),
      var2 = factor(var2, levels = rev(levs), labels = rev(labs)),
      sig = gsub('ns', '', sig)
    )

  pbase <- theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8),
      axis.text.y = element_text(size = 8),
      legend.position = c(0.5, 1.1),
      legend.direction = 'horizontal',
      plot.margin = unit(c(6,4,0,0), "lines"),
      strip.background = element_blank(),
      strip.text.y = element_text(angle = 0, hjust = 0, vjust = 0.5),
      panel.background = element_rect(fill = 'black')
    )

  outlab <- data.frame(
    y = c(1.5, 9.5),
    lab = c('Biological', 'Environment')
  )

  p <- ggplot(prplo) +
    geom_tile(aes(y = var1, x = var2, fill = cor), colour = 'black') +
    geom_text(aes(y = var1, x = var2, label = sig)) +
    annotation_custom(grob = textGrob(label = outlab$lab[1], hjust = 0, gp = gpar(cex = 0.7)),
                      ymin = outlab$y[1], ymax = outlab$y[1], xmin = 17, xmax = 17) +
    annotation_custom(grob = textGrob(label = outlab$lab[2], hjust = 0, gp = gpar(cex = 0.7)),
                      ymin = outlab$y[2], ymax = outlab$y[2], xmin = 17, xmax = 17) +
    annotation_custom(grob = textGrob(label = outlab$lab[1], hjust = 0.5, gp = gpar(cex = 0.7)),
                      xmin = outlab$y[1], xmax = outlab$y[1], ymin = 17, ymax = 17) +
    annotation_custom(grob = textGrob(label = outlab$lab[2], hjust = 0.5, gp = gpar(cex = 0.7)),
                      xmin = outlab$y[2], xmax = outlab$y[2], ymin = 17, ymax = 17) +
    pbase +
    scale_y_discrete('', expand = c(0, 0), labels = parse(text = rev(labs))) +
    scale_x_discrete('', expand = c(0, 0), labels = parse(text = rev(labs))) +
    scale_fill_gradient2('Correlation', low = muted("blue"), mid = "white", high = muted("red"), midpoint = 0) +
    geom_hline(yintercept = 3.5, size = 1.5) +
    geom_vline(xintercept = 3.5, size = 1.5)

  return(p)

})

# pca biplot
pcaplo1 <- reactive({
  
  # input
  dep1cor <- dep1cor()
  crvrs <- input$crvrs
  
  topca <- dep1cor %>% na.omit
  mod <- prcomp(topca[ , crvrs], scale = T, center = T)

  # no labels
  p <- ggord(mod, vec_ext = 5, size = topca$abundances, coord_fix = F, labcol = 'blue') + 
    scale_size(range = c(2, 8)) +
    guides(size = guide_legend(title = 'Abundances')) + 
    theme(legend.position = 'top')

  return(p)
  
})
```

# Correlation matrix and PCA biplot

```{r pairsplots, fig.height = 9, fig.width = 9}
renderPlot({
    
  corplo1() + pcaplo1() + plot_layout(ncol = 2)
  
}, height = 400, width = 800)
```

# Aggregate models

```{r}
##
# prep data for modelling

# model globals
fams <- list(
    abundances = 'gaussian',
    pa = 'binomial',
    length = 'gaussian', 
    dissolution = 'gaussian'
  ) %>%
  enframe('res', 'dist')

# data prep, nested for mods
tomod <- reactive({

  # input
  dep1 <- as.numeric(input$dep1)
  crbs_eval <- crbs_eval()
  crvrs <- input$crvrs
  logm <- input$logm

  # model formulas
  if(!as.logical(logm)){
    resp <- c(
      abundances = 'val',
      pa = 'val',
      length = 'val', 
      dissolution = 'val'
    )
  } else {
    resp <- c(
      abundances = 'log10(1+val)',
      pa = 'val',
      length = 'val', 
      dissolution = 'val'
    ) 
  }
  
  resp <- resp %>% 
    enframe('res', 'resp') %>%
    group_by(res) %>%
    nest(.key = 'resp') %>%
    mutate(
      resp = map(resp, ~ paste(.x, paste(crvrs, collapse = '+'), sep = '~'))
      )
  
  # join environmental and biological data
  out <- envdatdelt %>%
    filter(depth %in% c(dep1)) %>%
    dplyr::select_(.dots = c('depth', 'CTD', crvrs)) %>% 
    left_join(crbs_eval, by = 'CTD') %>%
    # gather('var', 'val', -CTD, -abundances, -pa, -length, -dissolution, -depth) %>%
    # group_by(var) %>%
    # mutate(
    #   val = scale(val, center = T, scale = F)
    # ) %>%
    # spread(var, val) %>%
    dplyr::select_(.dots = c('depth', 'abundances', 'pa', 'length', 'dissolution', crvrs)) %>%
    gather('res', 'val', abundances, pa, length, dissolution) %>%
    dplyr::select(depth, res, val, everything()) %>%
    group_by(depth, res) %>%
    nest %>%
    left_join(fams, by = 'res') %>%
    left_join(resp, by = 'res')

  return(out)
  
})

# check vif values for three variable models, by depth
vifchk <- reactive({
  
  # input
  tocor <- tocor()
  crvrs <- input$crvrs
  
  # get vif values
  out <- tocor %>% 
    dplyr::select_(.dots = c('depth', crvrs)) %>% 
    group_by(depth) %>% 
    nest %>% 
    mutate(
      vifchk = map(data, function(x){
        
        # get vif values for each var against the others
        val <- NULL
        for(i in names(x)){
          
          yval <- i
          xvals <- names(x)[!names(x) %in% i] %>% 
            paste(collapse = ' + ')
          
          frm <- formula(paste(yval, '~', xvals))
          mod <- lm(frm, x)
          rsq <- mod %>% 
            summary %>% 
            .$r.squared
          vif <- 1 / (1 - rsq)
          
          val <- c(val, vif)
          
        }
        
        # format vif values as data frame for unnest
        names(val) <- names(x)
        val <- val %>% 
          as.list %>% 
          data.frame %>% 
          round(1)
        
        return(val)
        
      })
    ) %>% 
    select(-data) %>% 
    unnest
  
  return(out)
  
})

##
# model selection

mods <- reactive({

  # input
  tomod <- tomod()

  tops <- vector('list', length = nrow(tomod))
  cffs <- vector('list', length = nrow(tomod))

  for(i in 1:nrow(tomod)){

    x <- tomod[i, ] %>%
      .[['data']] %>%
      .[[1]] %>%
      na.omit

    resp <- tomod[i, ] %>%
      pull(resp) %>%
      .[[1]]

    dist <- tomod[i, ] %>%
      pull(dist) %>%
      .[[1]]

    cffsmlt <- do.call('glmulti',
                    list(formula(resp), data = x, level = 1, method = 'h', crit = 'aicc', plotty = F, report = F, fitfunction = 'glm', family = dist)) %>%
      coef %>%
      data.frame %>%
      rownames_to_column('var')

    # global glm
    globs <- paste0('glm(', resp, ', data = x, na.action = na.pass, family = "', dist, '")') %>%
      parse(text = .) %>%
      eval

    # dredge, get sum stats manually
    drdg <- dredge(globs)
    maxmod <- pmin(nrow(drdg), 10)
    drdgsub <- get.models(drdg, subset = 1:maxmod) %>%
      map(., function(x){

        # get mod prm, pval
        out <- x %>% summary %>% coef %>% data.frame %>% rownames_to_column('var') %>%
          .[, c(1, 2, 5)]
        names(out)[3] <- 'pval'
        out <- out %>%
          mutate(
            Estimate = round(Estimate, 2),
            pval = p_ast(pval)
            ) %>%
          unite('Estimate', Estimate, pval, sep = '') %>%
          spread(var, Estimate)

        # get sum stats
        llk <- logLik(x)
        out <- out %>%
           mutate(
            df = attr(llk, 'df'),
            loglik = llk[1],
            aicc = aicc(x)
          )

        return(out)
      }) %>%
      enframe %>%
      unnest %>%
      mutate(
        model = 1:n(),
        delta = aicc - aicc[1]
        ) %>%
      select(model, df, loglik, aicc, delta, everything()) %>%
      select(-name) %>%
      gather('var', 'val', -model, -df, -loglik, -aicc, -delta) %>%
      spread(var, val, fill = NA) %>%
      mutate(
        aicc = round(aicc, 2),
        loglik = round(loglik, 2),
        delta = round(delta, 2)
      )

    tops[[i]] <- drdgsub
    cffs[[i]] <- cffsmlt

  }

  # models
  mods <- tomod %>%
    select(depth, res) %>%
    mutate(
      tops = tops,
      cffs = cffs
    )

  return(mods)

})

```

```{r fig.height = 8, fig.width = 8}
renderUI({

  HTML(knitr::kable(vifchk(), caption = 'VIF values for each variable relative to the others for models at the selected depths.', format = 'html') %>% 
    kable_styling(full_width = T, font_size = 14))
  
})

renderPlot({

  # input
  mods <- mods()

  # toplot
  toplo <- mods %>%
    select(-tops) %>%
    unnest %>%
    filter(!var %in% '(Intercept)') %>%
    mutate(
      `Depth (m)` = factor(depth),
      res = factor(res,
                   levels = c('abundances', 'pa', 'length', 'dissolution'),
                   labels = c('Abundance', 'Pres./Abs.', 'Length', 'Dissolution'))
      )
  names(toplo) <- gsub('\\.*', '', names(toplo))

  thm <- theme_bw(base_family = 'serif', base_size = 14) +
    theme(
      strip.background = element_blank(),
      legend.position = 'top',
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1)
    )

  # importance
  toplo1 <- toplo 
  
  p1 <- ggplot(toplo1, aes(x = var, y = Importance)) +
    geom_bar(stat = 'identity', position = 'dodge', colour = 'black') +
    facet_wrap(~ res, ncol = 1, scales = 'free_y') +
    thm +
    theme(legend.position = 'none') +
    ggtitle('Variable\nimportance')

  # estimates
  toplo2 <- toplo 
  
  p2 <- ggplot(toplo2, aes(x = var, y = Estimate)) +
    geom_bar(stat = 'identity', position = 'dodge', colour = 'black') +
    geom_hline(yintercept = 0) +
    facet_wrap(~ res, ncol = 1, scales = 'free_y') +
    thm +
    ggtitle('Pooled parameter\nestimates') 

  # unconditional variance
  toplo3 <- toplo
  p3 <- ggplot(toplo3, aes(x = var, y = Uncondvariance)) +
    geom_bar(stat = 'identity', position = 'dodge', colour = 'black') +
    facet_wrap(~ res, ncol = 1, scales = 'free_y') +
    thm +
    ggtitle('Unconditional explained\nvariance (%)')

  grid.arrange(
    p1, p3, p2, ncol = 3
  )

}, width = 700, height = 700)
```

Results of model selection analysis with three crab population variables (abundance, presence/absence, carapace length) by shallow and deep water. Variable importances and pooled estimates show summarized results from multiple models that evaluated all parameter combinations.  The unconditional explained variance (%) is the effect of each variable independent of all other variables.

# Top models in tabular {.tabset .tabset-pills}

```{r}
##
# tables of top mods

# tabular
totab <- reactive({

  mods() %>%
    select(-cffs)

})
```

## Abundance

```{r, results = 'asis'}
# abundance table
renderUI({

  # input
  totab <- totab()
  crvrs <- input$crvrs

  abutab <- totab %>%
    filter(res %in% 'abundances') %>%
    select(-res) %>%
    unnest %>%
    mutate(depth = paste(depth, 'm'))
  abutab[is.na(abutab)] <- '-'

  cap.val<-paste0('Top selected models for crab abundance at shallow and deep water. Input variables were ', paste(tolower(sort(crvrs)), collapse = ', '), '.')
  cap.val <- gsub('^(.*), (.*)$', '\\1, and \\2', cap.val)

  HTML(knitr::kable(abutab, caption = cap.val, format = 'html') %>% 
    kable_styling(full_width = T, font_size = 14))

})
```

## Presence/absence

```{r, results = 'asis'}
# pa table
renderUI({

  # input
  totab <- totab()
  crvrs <- input$crvrs

  patab <- totab %>%
    filter(res %in% 'pa') %>%
    select(-res) %>%
    unnest
  patab[is.na(patab)] <- '-'
  
  cap.val<-paste0('Top selected models for crab presence/absence at shallow and deep water. Input variables were ', paste(tolower(sort(crvrs)), collapse = ', '), '.')
  cap.val <- gsub('^(.*), (.*)$', '\\1, and \\2', cap.val)

  HTML(knitr::kable(patab, caption = cap.val, format = 'html')%>% 
    kable_styling(full_width = T, font_size = 14))

})
```

## Length

```{r, results = 'asis'}
# carapace length table
renderUI({

  # input
  totab <- totab()
  crvrs <- input$crvrs

  cltab <- totab %>%
    filter(res %in% 'length') %>%
    select(-res) %>%
    unnest
  cltab[is.na(cltab)] <- '-'

  cap.val<-paste0('Top selected models for crab carapace length at shallow and deep water. Input variables were ', paste(tolower(sort(crvrs)), collapse = ', '), '.')
  cap.val <- gsub('^(.*), (.*)$', '\\1, and \\2', cap.val)

  HTML(knitr::kable(cltab, caption = cap.val, format = 'html') %>% 
    kable_styling(full_width = T, font_size = 14))

})
```

## Dissolution

```{r, results = 'asis'}
# carapace length table
renderUI({

  # input
  totab <- totab()
  crvrs <- input$crvrs

  cltab <- totab %>%
    filter(res %in% 'dissolution') %>%
    select(-res) %>%
    unnest
  cltab[is.na(cltab)] <- '-'
  
  cap.val<-paste0('Top selected models for crab dissolution at shallow and deep water. Input variables were ', paste(tolower(sort(crvrs)), collapse = ', '), '.')
  cap.val <- gsub('^(.*), (.*)$', '\\1, and \\2', cap.val)

  HTML(knitr::kable(cltab, caption = cap.val, format = 'html') %>% 
    kable_styling(full_width = T, font_size = 14))

})
```


