---
title: "Exploration of crab dissolution"
author: ""
output: 
  html_document:
    css: kable.css
self_contained: yes
runtime: shiny
---

```{r, message = F, warning = F, echo = F}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, dev.args = list(bg = 'transparent', family = 'serif'), eval = T, echo = F)

library(tidyverse)
library(shiny)

source('R/funcs.R')

data(dissdat)
data(lengdat)
data(envdatdelt)
data(shoreloc)
data(crbs)

# abundance data
abudat <- crbs %>% 
  select(CTD, abundances) %>% 
  na.omit
```

```{r selectors}
column(12,
column(4, 
       
       selectInput('lng', 'Select length measure:', choices = unique(lengdat$lenvar))
       
       ),
column(4, 
       
       selectInput('dss', 'Select dissolution measure:', choices = unique(dissdat$distyp))
       
       ), 
column(4, 
      selectInput('logm', 'Log models (abundance only):', choices = c(TRUE, FALSE))
)
)
```

```{r reactives}
# combined dissolution, length data to plot, model
dislendat <- reactive({
  
  # input
  lng <- input$lng
  dss <- input$dss
  
  out <- inner_join(lengdat, dissdat, by = 'CTD') %>% 
    filter(lenvar %in% lng) %>% 
    filter(distyp %in% dss) 

  return(out)
  
})

# regression models in plot, length
dislenmod <- reactive({
  
  # input
  dislendat <- dislendat()

  ## model output
  
  # all data
  allmods <- dislendat %>% 
    group_by(prt) %>% 
    nest %>% 
    mutate(
      mod = map(data, function(x){
        
        lm(avelen ~ disval, data = x) %>% 
          summary
        
      }),
      dattyp = 'All data'
    )
  
  # onshore only
  onsmods <- dislendat %>% 
    filter(shoreloc %in% 'onshore') %>% 
    group_by(prt) %>% 
    nest %>% 
    mutate(
      mod = map(data, function(x){
        
        lm(avelen ~ disval, data = x) %>% 
          summary
        
      }),
      dattyp = 'On shore'
    )
  
  # combine models get summaries
  out <- rbind(allmods, onsmods) %>% 
    mutate(summod = map(mod, getsum)) %>% 
    select(prt, dattyp, summod) %>% 
    unnest %>% 
    arrange(prt, dattyp) %>% 
    rename(
      `Crab body location` = prt, 
      `Model subset` = dattyp
    )
  
  return(out)
  
})

# dissolution data plot, length
dislenplo <- reactive({
  
  # input
  dislendat <- dislendat()
  
  # plot
  p <- ggplot(dislendat, aes(x = disval, y = avelen)) +
    geom_point(aes(color = shoreloc), size = 4) + 
    geom_errorbar(aes(ymin = avelen - stelen, ymax = avelen + stelen, color = shoreloc), width = 0) +
    facet_grid(~prt) + 
    geom_smooth(method = 'lm', colour = 'black', se = F) + 
    geom_smooth(aes(group = shoreloc, linetype = shoreloc), colour = 'aquamarine3', se = F, method = 'lm') +
    theme_bw(base_family = 'serif', base_size = 16) +
    theme(
      legend.title = element_blank(),
      strip.background = element_blank(),
      legend.position = 'top'
      ) +
    scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
    ylab('Length') + 
    xlab('Dissolution') +
    scale_linetype_manual(values = c(0, 2))
  
  return(p)

})

# combined dissolution, abundance data to plot, model
disabudat <- reactive({
  
  # input
  dss <- input$dss
  loc <- input$loc
  
  abudat <- crbs %>% 
    select(CTD, abundances) %>% 
    na.omit

  out <- inner_join(abudat, dissdat, by = 'CTD') %>% 
    left_join(shoreloc, by = 'CTD') %>% 
    filter(distyp %in% dss) 
  return(out)
  
})

# regression models in plot, abundance
disabumod <- reactive({
  
  # input
  disabudat <- disabudat()
  logm <- input$logm
  ## model output
  
  # all data
  allmods <- disabudat %>% 
    group_by(prt) %>% 
    nest %>% 
    mutate(
      mod = map(data, function(x){
        
        if(logm)
          modout <- lm(log10(abundances) ~ disval, data = x)
        else 
          modout <- lm(abundances ~ disval, data = x)
        
        summary(modout)
        
      }),
      dattyp = 'All data'
    )
  
  # onshore only
  onsmods <- disabudat %>% 
    filter(shoreloc %in% 'onshore') %>% 
    group_by(prt) %>% 
    nest %>% 
    mutate(
      mod = map(data, function(x){
        
        if(logm)
          modout <- lm(log10(abundances) ~ disval, data = x)
        else 
          modout <- lm(abundances ~ disval, data = x)
        
        summary(modout)
        
      }),
      dattyp = 'On shore'
    )
  
  # combine models get summaries
  out <- rbind(allmods, onsmods) %>% 
    mutate(summod = map(mod, getsum)) %>% 
    select(prt, dattyp, summod) %>% 
    unnest %>% 
    arrange(prt, dattyp) %>% 
    rename(
      `Crab body location` = prt, 
      `Model subset` = dattyp
    )
    
  return(out)
  
})

# dissolution data plot, abundance
disabuplo <- reactive({
  
  # input
  disabudat <- disabudat()
  logm <- input$logm
  
  # plot
  p <- ggplot(disabudat, aes(x = disval, y = abundances)) +
    geom_point(aes(color = shoreloc), size = 4) + 
    facet_grid(~prt) + 
    geom_smooth(method = 'lm', colour = 'black', se = F) + 
    geom_smooth(aes(group = shoreloc, linetype = shoreloc), colour = 'aquamarine3', se = F, method = 'lm') +
    theme_bw(base_family = 'serif', base_size = 16) +
    theme(
      legend.title = element_blank(),
      strip.background = element_blank(),
      legend.position = 'top'
      ) +
    scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
    ylab('Counts') + 
    xlab('Dissolution') +
    scale_linetype_manual(values = c(0, 2))
  
  if(logm)
    p <- p + scale_y_log10('log-Counts')
  
  return(p)
})

# combined length, abundance data to plot, model
lenabudat <- reactive({
  
  # input
  lng <- input$lng
  
  out <- inner_join(abudat, lengdat, by = 'CTD') %>% 
    filter(lenvar %in% lng) 

  return(out)
  
})

# regression models in plot, abundance and length
lenabumod <- reactive({
  
  # input
  lenabudat <- lenabudat()
  logm <- input$logm

  ## model output

  # all data
  allmods <- lenabudat %>% 
    nest %>% 
    mutate(
      mod = map(data, function(x){
        
        if(logm)
          modout <- lm(log10(abundances) ~ avelen, data = x)
        else 
          modout <- lm(abundances ~ avelen, data = x)
        
        summary(modout)
        
      }),
      dattyp = 'All data'
    )
  
  # onshore only
  onsmods <- lenabudat %>% 
    filter(shoreloc %in% 'onshore') %>% 
    nest %>% 
    mutate(
      mod = map(data, function(x){
        
        if(logm)
          modout <- lm(log10(abundances) ~ avelen, data = x)
        else 
          modout <- lm(abundances ~ avelen, data = x)
        
        summary(modout)
        
      }),
      dattyp = 'On shore'
    )
  
  # combine models get summaries
  out <- rbind(allmods, onsmods) %>% 
    mutate(summod = map(mod, getsum)) %>%
    select(dattyp, summod) %>% 
    unnest %>% 
    arrange(dattyp) %>% 
    rename(
      `Model subset` = dattyp
    )
    
  return(out)
  
})

# dissolution data plot, abundance, length
lenabuplo <- reactive({
  
  # input
  lenabudat <- lenabudat()
  logm <- input$logm
  
  # plot
  p <- ggplot(lenabudat, aes(x = avelen, y = abundances)) +
    geom_point(aes(color = shoreloc), size = 4) + 
    geom_errorbarh(aes(xmin = avelen - stelen, xmax = avelen + stelen, color = shoreloc), height = 0) +
    geom_smooth(method = 'lm', colour = 'black', se = F) + 
    geom_smooth(aes(group = shoreloc, linetype = shoreloc), colour = 'aquamarine3', se = F, method = 'lm') +
    theme_bw(base_family = 'serif', base_size = 16) +
    theme(
      legend.title = element_blank(),
      strip.background = element_blank(),
      legend.position = 'top'
      ) +
    scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
    ylab('Counts') + 
    xlab('Length') +
    scale_linetype_manual(values = c(0, 2))
  
  if(logm)
    p <- p + scale_y_log10('log-Counts')
  
  return(p)

})

# environmental data for selected depth
envdep <- reactive({
  
  # inputs
  dep <- input$dep
  
  out <- envdatdelt %>% 
    filter(depth %in% dep) %>% 
    select(-depth) %>% 
    gather('valtyp', 'val', val, delt) %>% 
    unite('var', var, valtyp, sep = '') %>% 
    mutate(var = gsub('val$', '', var)) %>% 
    filter(var %in% c('Aragonite', 'Temperature', 'pH', 'pHdelt'))
  
  return(out)
  
})

# dissolution data with environmental data
disenvdat <- reactive({
  
  # input
  envdep <- envdep()
  dss <- input$dss

  out <- inner_join(envdep, dissdat, by = 'CTD') %>% 
    filter(distyp %in% dss) %>% 
    left_join(shoreloc, by = 'CTD')

  return(out)
  
})

# dissolution models with environmental data
disenvmod <- reactive({

  # input
  disenvdat <- disenvdat()

  ## model output

  # all data
  allmods <- disenvdat %>%
    group_by(var, prt) %>% 
    nest %>%
    mutate(
      mod = map(data, function(x){

        modout <- lm(disval ~ val, data = x)
        summary(modout)

      }),
      dattyp = 'All data'
    )

  # onshore only
  onsmods <- disenvdat %>%
    group_by(var, prt) %>% 
    filter(shoreloc %in% 'onshore') %>%
    nest %>%
    mutate(
      mod = map(data, function(x){

        modout <- lm(disval ~ val, data = x)
        summary(modout)

      }),
      dattyp = 'On shore'
    )

  # combine models get summaries
  out <- rbind(allmods, onsmods) %>%
    mutate(summod = map(mod, getsum)) %>%
    select(var, prt, dattyp, summod) %>%
    unnest %>%
    arrange(var, prt, dattyp) %>%
    rename(
      `Crab body location` = prt, 
      `Model subset` = dattyp, 
      `Environmental variable` = var
    )

  return(out)
  
})

# dissolution data plot, environment
disenvplo <- reactive({
  
  # input
  disenvdat <- disenvdat()

  # plot
  p <- ggplot(disenvdat, aes(x = val, y = disval)) +
    geom_point(aes(color = shoreloc), size = 4) + 
    facet_grid(prt ~ var, scales = 'free_x') + 
    geom_smooth(method = 'lm', colour = 'black', se = F) + 
    geom_smooth(aes(group = shoreloc, linetype = shoreloc), colour = 'aquamarine3', se = F, method = 'lm') +
    theme_bw(base_family = 'serif', base_size = 16) +
    theme(
      legend.title = element_blank(),
      strip.background = element_blank(),
      legend.position = 'top'
      ) +
    scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
    ylab('Dissolution') + 
    xlab('Environmental variable') +
    scale_linetype_manual(values = c(0, 2))
  
  return(p)
  
})

# length data with environmental data
lenenvdat <- reactive({
  
  # input
  envdep <- envdep()
  lng <- input$lng

  out <- inner_join(envdep, lengdat, by = 'CTD') %>% 
    filter(lenvar %in% lng)

  return(out)
  
})

# length models with environmental data
lenenvmod <- reactive({

  # input
  lenenvdat <- lenenvdat()

  ## model output

  # all data
  allmods <- lenenvdat %>%
    group_by(var) %>% 
    nest %>%
    mutate(
      mod = map(data, function(x){

        modout <- lm(avelen ~ val, data = x)
        summary(modout)

      }),
      dattyp = 'All data'
    )

  # onshore only
  onsmods <- lenenvdat %>%
    group_by(var) %>% 
    filter(shoreloc %in% 'onshore') %>%
    nest %>%
    mutate(
      mod = map(data, function(x){

        modout <- lm(avelen ~ val, data = x)
        summary(modout)

      }),
      dattyp = 'On shore'
    )

  # combine models get summaries
  out <- rbind(allmods, onsmods) %>%
    mutate(summod = map(mod, getsum)) %>%
    select(var, dattyp, summod) %>%
    unnest %>%
    arrange(var, dattyp) %>%
    rename(
      `Model subset` = dattyp, 
      `Environmental variable` = var
    )

  return(out)
  
})

# length data plot, environment
lenenvplo <- reactive({
  
  # input
  lenenvdat <- lenenvdat()

  # plot
  p <- ggplot(lenenvdat, aes(x = val, y = avelen)) +
    geom_point(aes(color = shoreloc), size = 4) + 
    geom_errorbar(aes(ymin = avelen - stelen, ymax = avelen + stelen, color = shoreloc), width = 0) +
    facet_grid( ~ var, scales = 'free_x') + 
    geom_smooth(method = 'lm', colour = 'black', se = F) + 
    geom_smooth(aes(group = shoreloc, linetype = shoreloc), colour = 'aquamarine3', se = F, method = 'lm') +
    theme_bw(base_family = 'serif', base_size = 16) +
    theme(
      legend.title = element_blank(),
      strip.background = element_blank(),
      legend.position = 'top'
      ) +
    scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
    ylab('Length') + 
    xlab('Environmental variable') +
    scale_linetype_manual(values = c(0, 2))
  
  return(p)
  
})

# abundance data with environmental data
abuenvdat <- reactive({
  
  # input
  envdep <- envdep()
  lng <- input$lng
  
  out <- inner_join(envdep, abudat, by = 'CTD') %>% 
    left_join(shoreloc, by = 'CTD') %>% 
    filter(!is.na(shoreloc))
  
  return(out)
  
})

# regression models in plot, abundance
abuenvmod <- reactive({
  
  # input
  abuenvdat <- abuenvdat()
  logm <- input$logm

  ## model output
  
  # all data
  allmods <- abuenvdat %>% 
    group_by(var) %>% 
    nest %>% 
    mutate(
      mod = map(data, function(x){
        
        if(logm)
          modout <- lm(log10(1 + abundances) ~ val, data = x)
        else 
          modout <- lm(abundances ~ val, data = x)
        
        summary(modout)
        
      }),
      dattyp = 'All data'
    )
  
  # onshore only
  onsmods <- abuenvdat %>% 
    filter(shoreloc %in% 'onshore') %>% 
    group_by(var) %>% 
    nest %>% 
    mutate(
      mod = map(data, function(x){
        
        if(logm)
          modout <- lm(log10(abundances) ~ val, data = x)
        else 
          modout <- lm(abundances ~ val, data = x)
        
        summary(modout)
        
      }),
      dattyp = 'On shore'
    )
  
  # combine models get summaries
  out <- rbind(allmods, onsmods) %>% 
    mutate(summod = map(mod, getsum)) %>% 
    select(var, dattyp, summod) %>% 
    unnest %>% 
    arrange(var, dattyp) %>% 
    rename(
      `Environmental variable` = var,
      `Model subset` = dattyp
    )
    
  return(out)
  
})

# aundance data plot, environment
abuenvplo <- reactive({
  
  # input
  logm <- input$logm
  abuenvdat <- abuenvdat()

  # plot
  p <- ggplot(abuenvdat, aes(x = val, y = abundances)) +
    geom_point(aes(color = shoreloc), size = 4) + 
    facet_grid( ~ var, scales = 'free_x') + 
    geom_smooth(method = 'lm', colour = 'black', se = F) + 
    geom_smooth(aes(group = shoreloc, linetype = shoreloc), colour = 'aquamarine3', se = F, method = 'lm') +
    theme_bw(base_family = 'serif', base_size = 16) +
    theme(
      legend.title = element_blank(),
      strip.background = element_blank(),
      legend.position = 'top'
      ) +
    scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
    ylab('Counts') + 
    xlab('Environmental variable') +
    scale_linetype_manual(values = c(0, 2))
  
  if(logm)
    p <- p + scale_y_log10('log-Counts')
  
  return(p)
  
})

# presence absence data with environmental data
prsenvdat <- reactive({
  
  # input
  envdep <- envdep()
  
  out <- inner_join(envdep, abudat, by = 'CTD') %>% 
    mutate(prs = ifelse(abundances > 0, 1, 0)) %>% 
    select(-abundances)
  
  return(out)
  
})

# regression models in plot, presence absence
prsenvmod <- reactive({
  
  # input
  prsenvdat <- prsenvdat()

  ## model output
  
  # all data
  allmods <- prsenvdat %>% 
    group_by(var) %>% 
    nest %>% 
    mutate(
      mod = map(data, function(x){
        
        modout <- glm(prs ~ val, family = binomial(link = 'logit'), data = x)
        modout
        
      }),
      dattyp = 'All data'
    )

  # combine models get summaries
  out <- allmods %>% 
    mutate(summod = map(mod, getsum)) %>% 
    select(var, dattyp, summod) %>% 
    unnest %>% 
    arrange(var, dattyp) %>% 
    rename(
      `Environmental variable` = var,
      `Model subset` = dattyp
    )
    
  return(out)
  
})

# aundance data plot, environment
prsenvplo <- reactive({
  
  # input
  prsenvdat <- prsenvdat()

  # plot
  p <- ggplot(prsenvdat, aes(x = val, y = prs)) +
    geom_point(size = 4, alpha = 0.7) + 
    facet_grid( ~ var, scales = 'free_x') + 
    geom_smooth(method = "glm", method.args = list(family = "binomial")) +
    theme_bw(base_family = 'serif', base_size = 16) +
    theme(
      legend.title = element_blank(),
      strip.background = element_blank(),
      legend.position = 'top'
      ) +
    ylab('Presence/absence') + 
    xlab('Environmental variable')
  
  return(p)
  
})

```
## {.tabset} 

### Length vs dissolution 

These plots show the relationship between dissolution and length for the selected measures above.  Each point is based on an aggregated dissolution measure (as an average from three replicates) and the corresponding lengths for the same station.  The length values are also aggregated but represent average length across multiple individuals that were collected at a station.  The error bars around the length represent 95% confidence intervals for the length measurements.  The regression lines were fit for the average dissolution and length measurements, where the black line is for all points and the dotted line is fit only for sites identified as onshore.  

```{r}
renderPlot({dislenplo()}, height = 300, width = 900)
```

The table shows summary statistics for each linear model in the above plot.  The crab body location is where the dissolution was measured (plot facets) and the model subset indicates the appropriate regression model in each plot facet.  The summary information are F-statistics (`F.stat`, whole model), p-value (`p.mod`, whole model), R-squared (`R2`), `slope` (slope estimate for length vs dissolution), t-statistic (`t.stat`, test statistics for slope), and p-value (`p.slope`, significance of slope). ns: p >= 0.05, \* p < 0.05, ** p < 0.01
```{r}
renderTable({dislenmod()})
```

### Abundance vs dissolution

These plots show the relationship between dissolution and abundance for the selected measures above.  Each point is based on an aggregated dissolution measure (as an average from three replicates) and the corresponding abundance (count) for the same station.  The regression lines were fit for the average dissolution and abundance measurements, where the black line is for all points and the dotted line is fit only for sites identified as onshore.  

```{r}
renderPlot({disabuplo()}, height = 300, width = 900)
```

The table shows summary statistics for each linear model in the above plot.  The crab body location is where the dissolution was measured (plot facets) and the model subset indicates the appropriate regression model in each plot facet.  The summary information are F-statistics (`F.stat`, whole model), p-value (`p.mod`, whole model), R-squared (`R2`), `slope` (slope estimate for abundance vs dissolution), t-statistic (`t.stat`, test statistics for slope), and p-value (`p.slope`, significance of slope). ns: p >= 0.05, \* p < 0.05, ** p < 0.01
```{r}
renderTable({disabumod()})
```

### Abundance vs length

Each point is based on an crab counts and the corresponding lengths for the same station.  The length values are also aggregated but represent average length across multiple individuals that were collected at a station.  The error bars around the length represent 95% confidence intervals for the length measurements.  The regression lines were fit for the counts and average length measurements, where the black line is for all points and the dotted line is fit only for sites identified as onshore.  

```{r}
renderPlot({lenabuplo()}, height = 300, width = 300)
```

The table shows summary statistics for each linear model in the above plot.  The model subset indicates the appropriate regression model in each plot facet.  The summary information are F-statistics (`F.stat`, whole model), p-value (`p.mod`, whole model), R-squared (`R2`), `slope` (slope estimate for abundance vs length), t-statistic (`t.stat`, test statistics for slope), and p-value (`p.slope`, significance of slope). ns: p >= 0.05, \* p < 0.05, ** p < 0.01
```{r}
renderTable({lenabumod()})
```

### Environmental data {.tabset .tabset-pills}

These tabs show the relationships of environmental variables with dissolution, length, and abundances. The drop-down menu below can be used to select environmental data from a specific depth.  Values for delta-pH are based on the difference between the observed value at the selected depth and that at the surface.  Stations 109 and 128 are excluded in the analysis because environmental data were unavailable.  

```{r}
selectInput('dep', 'Select depth for environment:', choices = sort(unique(envdatdelt$depth)), selected = 50)
```

#### Dissolution

```{r}
renderPlot({disenvplo()},height = 700, width = 800)
```

```{r}
renderTable({disenvmod()})
```

#### Length

```{r}
renderPlot({lenenvplo()},height = 300, width = 900)
```

```{r}
renderTable({lenenvmod()})
```

#### Abundance

```{r}
renderPlot({abuenvplo()},height = 300, width = 900)
```

```{r}
renderTable({abuenvmod()})
```

#### Presence/absence

```{r}
renderPlot({prsenvplo()},height = 300, width = 900)
```

```{r}
renderTable({prsenvmod()})
```