---
title: "Exploration of crab dissolution"
author: ""
output: 
  html_document:
    code_folding: hide
    css: kable.css
self_contained: yes
---

```{r, message = F, warning = F}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, dev.args = list(bg = 'transparent', family = 'serif'), eval = T)

library(tidyverse)
library(readxl)
library(ggord)
library(vegan)

source('R/funcs.R')

# environment data 100m, 30m
envall<- read_excel('raw/WCOA16_depth_limited_stats.xlsx') %>% 
  select(matches(c("^CTD Station$|100 m MEAN"))) %>% 
  rename(
    CTD = `CTD Station`, 
    arag = `Arag to 100 m MEAN`,
    ph = `pH to 100 m MEAN`,
    oxy = `Oxy [umol/kg] to 100 m MEAN`, 
    temp = `T [deg C] to 100 m MEAN`,
    alk = `TA [umol/kg] to 100 m MEAN`
  ) %>% 
  mutate_if(is.character, as.numeric)

# crab dissolution data joined with env data
toeval <- read_excel('raw/crab_diss.xlsx') %>% 
  rename(
    dissval = `Outside carapace`,
    disscat = qualitative
    ) %>% 
  mutate(
    disscat = factor(disscat, levels = c('lo', 'hi'), labels = c(0, 1)),
    disscat = as.numeric(as.character(disscat))
    ) %>% 
  left_join(envall, by = 'CTD') 
```

Plot environmental variables by categories.
```{r}
# prepped for first plot
toplo <- toeval %>% 
  gather('var', 'val', -CTD, -dissval, -disscat)

ggplot(toplo, aes(x = factor(disscat), y =val)) + 
  geom_boxplot() + 
  facet_wrap(~var, scales = 'free_y') + 
  scale_x_discrete('Dissolution', labels = c('less', 'a lot'))

```

```{r}
tst <- toplo %>% 
  group_by(var) %>% 
  nest %>% 
  mutate(
    tst = map(data, function(x){
      
      tst <- t.test(val ~ disscat, x)
      return(tst)
      
      }),
    tstglm = map(data, function(x){
      
      tstglm <- glm(disscat ~ val, x, family = 'binomial') %>% summary
      return(tstglm)
      
    }),
    tstaov = map(data, function(x){
      
      x$val <- cut(x$val, breaks = c(-Inf, median(x$val, na.rm = T), Inf), labels = c('lo', 'hi'))
      tstaov <- aov(dissval ~ val, x) %>% summary
      return(tstaov)
      
    })
  ) %>% 
  select(-data)
```

Wilcox (non-parameteric t-test) of differences in environmental variables by dissolution categories:
```{r}
ttst <- tst %>% 
  select(var, tst) %>% 
  deframe
ttst
```

GLM testing effects of environmental variables on likelihood of less, a lot dissolution categories:
```{r}
tstglm <- tst %>% 
  select(var, tstglm) %>% 
  deframe
tstglm
```

Analysis of variance evaluating continuous dissolution measures against lo/hi categories for environmental variables:
```{r}
tstaov <- tst %>%
  select(var, tstaov) %>% 
  deframe
tstaov
```

Testing pairwise effects (temp + alk, temp x alk, temp + ph, temp x ph):
```{r}
glm(disscat ~ temp + alk, data = toeval, family = 'binomial') %>% 
  summary
glm(disscat ~ temp * alk, data = toeval, family = 'binomial') %>% 
  summary
glm(disscat ~ temp + ph, data = toeval, family = 'binomial') %>% 
  summary
glm(disscat ~ temp * ph, data = toeval, family = 'binomial') %>% 
  summary
```

Principle components analysis and regression for combined environmental variables:
```{r}
pcaxs <- toeval %>% 
  select(-CTD, -dissval, -disscat) %>% 
  mutate_all(scale) %>% 
  prcomp %>% 
  .$x %>% 
  data.frame
pcaxs <- toeval %>% bind_cols(pcaxs)
glm(dissval ~ PC1 + PC2, data = pcaxs, family = 'gaussian') %>% summary
glm(disscat ~ PC1 + PC2, data = pcaxs, family = 'binomial') %>% summary
```

