---
output: 
  bookdown::html_document2:
    code_folding: hide
---

```{r message = F, warning = F, results = 'hide',echo=F}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, fig.path = 'figs/', dev.args = list(family = 'serif'))

library(tidyverse)
library(patchwork)
library(ggrepel)
library(vegan)
library(ggord)
library(grid)
library(gridExtra)
library(scales)

prj <- 4326 # wgs84

source('R/funcs.R')

pbase <- theme_bw(base_size = 12, base_family = 'serif') + 
  theme(
    # axis.title = element_blank(), 
    strip.background = element_blank() 
  ) 

data(dissdat)
data(crbs)
data(lengdat)
data(envdatdelt)
data(shoreloc)

# get all values and only ph delt
envdatdelt <- envdatdelt %>% 
  gather('envtyp', 'envval', val, delt) %>% 
  unite('var', var, envtyp, sep = '') %>% 
  filter(grepl('val$|^pHdelt|^Calcitedelt$', var)) %>% 
  mutate(var = gsub('\\val$', '', var)) %>% 
  rename(val = envval) %>% 
  mutate(
    val = ifelse(var %in% 'Chla', log10(val), val)
  )
```

# Figures and tables {.tabset}

## Layout

Review comments received from PNAS indicated that the environmental data and results from elemental analysis (Fig. S6) were the most interesting contributions of the manuscript.  Let's consider restructuring the text to emphasize these results.  

Introduction needs to describe lack of in situ data on environmental conditions that are relevant for evaluating larval response to low pH conditions - it hints at this but should be elaborated.  Also emphasize that we do not have a consistent methodology for measuring larval response to low pH, i.e., we need a consistent methodology for measure dissolution.  This will setup the rest of the text to highlight our environmental results and how the method for measuring dissolution is novel and leads to more insight (e.g., elemental results).

1) Figure: study sites map
1) Dissolution results: need to combine old figures 2, 4, S1, S2 in a way to show what information is obtained with the new method, reviewers commented that the info provided by each figure was unclear
1) Elemental mapping: old Figure S6 but need to present more clearly
1) Exploratory RDA plot for bio response and environmental variables
1) Environmental data: maps, PCA, gradients, by depth (old S3 but with clarity)
1) Correlation matrices: environmental v biological data
1) Regression plots: dissolution measures vs each other (e.g., how is external related to internal), dissolution measures vs environmental gradients
1) Regression plots: dissolution vs carapace width

Tables can also be provided to support regression results in the figures.


## Table 1

Summary of environmental data at 60 m for sites that are onshore (less than 200 m depth) and those that are offshore (greater than 200 m depth).  
```{r}
totab <- envdatdelt %>% 
  mutate(
    val = ifelse(var %in% 'Chla', 10 ^ val, val) # back-transform chla for table
  ) %>% 
  filter(CTD %in% dissdat$CTD) %>% 
  filter(depth %in% 60) %>% 
  left_join(shoreloc, by = 'CTD') %>% 
  select(-depth) %>% 
  group_by(var, shoreloc) %>% 
  summarise(
    avev = mean(val, na.rm = T), 
    medv = median(val, na.rm = T), 
    minv = min(val, na.rm = T), 
    maxv = max(val, na.rm = T)
  ) %>% 
  ungroup %>% 
  gather('varv', 'valv', -var, -shoreloc) %>% 
  mutate(
    valv = ifelse(var %in% c('Oxygen', 'Temperature', 'pCO2'), round(valv, 1), round(valv, 2)),
    valv = as.character(valv)
  ) %>% 
  spread(varv, valv) %>% 
  arrange(desc(shoreloc), var) %>% 
  mutate(
    shoreloc = factor(shoreloc, levels = c('onshore', 'offshore'), labels = c('Onshore', 'Offshore')),
    shoreloc = as.character(shoreloc),
    shoreloc = ifelse(duplicated(shoreloc), '', shoreloc)
  ) %>% 
  dplyr::select(shoreloc, var, avev, medv, minv, maxv) %>% 
  rename(
    Location = shoreloc,
    Parameter = var,
    Average = avev,
    Median = medv,
    Minimum = minv,
    Maximum = maxv
  )

knitr::kable(totab)
```

## Figure 1

[download](figs/regplot.jpg)

```{r regplot, fig.height = 7, fig.width = 7, fig.cap = ''}

envplo <- envdatdelt %>% 
  filter(var %in% c('pHdelt', 'pH')) %>% 
  filter(depth %in% 60) %>% 
  filter(CTD %in% crbs$CTD) %>% 
  dplyr::select(CTD, var, val) %>% 
  spread(var, val)

displo <- dissdat %>% 
  spread(prt, disval) %>% 
  # filter(!CTD %in% 109) %>%
  mutate(
    external = (`body part` + legs) / 2
  ) %>% 
  # gather('var', 'val', internal, external) %>% 
  # mutate(val = scales::rescale(val)) %>% 
  # spread(var, val) %>% 
  select(CTD, internal, external)

lenplo <- lengdat %>% 
  filter(lenvar %in% 'CW') %>% 
  dplyr::select(CTD, avelen)

toplo <- displo %>% 
  left_join(lenplo, by = 'CTD') %>% 
  left_join(envplo, by = 'CTD') %>% 
  left_join(shoreloc, by = 'CTD')

p1 <- ggplot(toplo, aes(x = pHdelt, y = external, colour = shoreloc)) + 
  geom_point(size = 2.5, alpha = 0.8) + 
  pbase + 
  theme(
    legend.title = element_blank(), 
    legend.position = 'none'
    ) + 
  scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
  xlab(expression(paste(Delta, 'pH'[60]))) +
  ylab('Relative external dissolution') +
  # scale_y_continuous(limits = c(0, 1)) +
  geom_smooth(method = 'lm', se = F, linetype = 'dashed', colour = 'black') + 
  geom_text_repel(aes(label = CTD), size = 3, show.legend = F) + 
  guides(text) +
  ggtitle('(a)') 

p2 <- ggplot(toplo, aes(x = pH, y = internal, colour = shoreloc)) + 
  geom_point(size = 2.5, alpha = 0.8) + 
  pbase + 
  theme(
    legend.title = element_blank(), 
    legend.position = 'none'
    ) + 
  scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
  xlab(expression(paste('pH'[60]))) +
  ylab('Relative internal dissolution') +
  # scale_y_continuous(limits = c(0, 1)) +
  geom_smooth(method = 'lm', se = F, linetype = 'dashed', colour = 'black') + 
  geom_text_repel(aes(label = CTD), size = 3, show.legend = F) + 
  guides(text) +
  ggtitle('(b)') 

p3 <- ggplot(toplo, aes(x = internal,  y = external, colour = shoreloc)) + 
  geom_point(size = 2.5, alpha = 0.8) + 
  xlab('Relative internal dissolution') + 
  ylab('Relative external dissolution') + 
  geom_abline(slope = 1, intercept = 0) + 
  pbase + 
  theme(
    legend.title = element_blank(), 
    legend.position = 'none'
    ) + 
  scale_y_continuous(limits = c(0, 1)) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
  geom_smooth(method = 'lm', se = F, linetype = 'dashed', colour = 'black') + 
  geom_text_repel(aes(label = CTD), size = 3, show.legend = F) + 
  ggtitle('(c)') 


onshoredat <- toplo %>% 
  filter(shoreloc %in% 'onshore')
p4 <- ggplot(toplo, aes(x = external,  y = avelen, colour = shoreloc)) + 
  geom_point(size = 2.5, alpha = 0.8) +  
  xlab('Relative external dissolution') + 
  ylab('Carapace width') + 
  pbase + 
  theme(
    legend.title = element_blank(), 
    legend.position = 'top'
    ) + 
  # scale_y_continuous(limits = c(0, 1)) + 
  # scale_x_continuous(limits = c(0, 1)) +
  scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
  geom_smooth(method = 'lm', se = F, linetype = 'dashed', colour = 'black') + 
  geom_smooth(data = onshoredat, method = 'lm', se= F, linetype = 'solid', colour = 'aquamarine3',alpha = 0.7) +
  geom_text_repel(aes(label = CTD), size = 3, show.legend = F) + 
  ggtitle('(d)') 

pleg <- g_legend(p4)
p4 <- p4 + theme(legend.position = 'none')

wrap_elements(pleg) + (p1 + p2 + p3 + p4 + plot_layout(ncol = 2)) + plot_layout(ncol = 1, heights = c(0.05, 1))
```

Panel a:
```{r}
lm(external ~ pHdelt, data = toplo) %>% summary
```

Panel b:
```{r}
lm(internal ~ pH, data = toplo) %>% summary
```

Panel c:
```{r}
lm(external ~ internal, data = toplo) %>% summary
```

Panel d:
```{r}
lm(avelen ~ external, data = onshoredat) %>% summary
```

### Internal dissolution and pH

```{r}
# dissolution predictions for internal, 10m model, onshore only

envplo <- envdatdelt %>% 
  filter(var %in% c('pHdelt', 'pH')) %>% 
  filter(depth %in% 10) %>% 
  filter(CTD %in% crbs$CTD) %>% 
  dplyr::select(CTD, var, val) %>% 
  spread(var, val)

displo <- dissdat %>% 
  spread(prt, disval) %>% 
  # filter(!CTD %in% 109) %>%
  mutate(
    external = (`body part` + legs) / 2
  ) %>% 
  # gather('var', 'val', internal, external) %>% 
  # mutate(val = scales::rescale(val)) %>% 
  # spread(var, val) %>% 
  select(CTD, internal, external)

lenplo <- lengdat %>% 
  filter(lenvar %in% 'CW') %>% 
  dplyr::select(CTD, avelen)

toplo <- displo %>% 
  left_join(lenplo, by = 'CTD') %>% 
  left_join(envplo, by = 'CTD') %>% 
  left_join(shoreloc, by = 'CTD') %>% 
  filter(shoreloc %in% 'onshore')

phmod <- lm(internal ~ pH, toplo)

df <- data.frame(
    pH = c(8.17, 8.043, 7.92, 7.82), 
    lab = c('pre-industrial', 'current', 'future45', 'future85')
  ) %>% 
  mutate(
    internal = predict(phmod, newdata = ., se.fit = T)$fit,
    sefit = predict(phmod, newdata = ., se.fit = T)$se.fit, 
    perchg = (internal - subset(internal, lab == 'current')) / subset(internal, lab == 'current')
  )
df
```

### External dissolution and delta pH

Baseline pHdelt is mean of phDelt observations for 60m.  Pre-industrial is the baseline phDelt - 2 \* 0.02 (estimated decadal change for two decades prior).   Post-industrial is the baseline phDelt + 2 \* 0.02 (estimated decadal change for 2 decades post)
```{r}
# dissolution predictions for external, deltph model, onshore only, 60 m

envplo <- envdatdelt %>% 
  filter(var %in% c('pHdelt', 'pH')) %>% 
  filter(depth %in% 60) %>% 
  # filter(CTD %in% crbs$CTD) %>% 
  dplyr::select(CTD, var, val) %>% 
  spread(var, val)

displo <- dissdat %>% 
  spread(prt, disval) %>% 
  # filter(!CTD %in% 109) %>%
  mutate(
    external = (`body part` + legs) / 2
  ) %>% 
  select(CTD, internal, external)

lenplo <- lengdat %>% 
  filter(lenvar %in% 'CW') %>% 
  dplyr::select(CTD, avelen)

toplo <- displo %>% 
  left_join(lenplo, by = 'CTD') %>% 
  left_join(envplo, by = 'CTD') %>% 
  left_join(shoreloc, by = 'CTD') %>% 
  filter(shoreloc %in% 'onshore')

phdeltmod <- lm(external ~ pHdelt, toplo)

decchn <- 0.02
bsedlt <- mean(envplo$pHdelt)
df <- data.frame(
    pHdelt = c(bsedlt - 2 * 0.02, bsedlt, bsedlt + 2 * 0.02), 
    lab = c('pre-industrial', 'current', 'future')
  ) %>% 
  mutate(
    external = predict(phdeltmod, newdata = ., se.fit = T)$fit,
    sefit = predict(phdeltmod, newdata = ., se.fit = T)$se.fit, 
    perchg = (external - subset(external, lab == 'current')) / subset(external, lab == 'current')
  )
df
```

## Figure 2

[download](figs/rdaplot.jpg)

```{r rdaplot, fig.height = 4, fig.width = 4}
datbio<- dissdat %>% 
  # filter(!CTD %in% c(109)) %>%
  spread(prt, disval) %>% 
  mutate(
    external = `body part` + legs
  ) %>% 
  select(CTD, internal, external)

lengdatsub <- lengdat %>% 
  filter(lenvar %in% 'CW')

datbio <- datbio %>% 
  left_join(lengdatsub, by = 'CTD') %>% 
  select(CTD, internal, external, avelen) %>% 
  gather('var', 'val', internal, external, avelen) %>% 
  group_by(var) %>% 
  mutate(val = ifelse(is.na(val), mean(val, na.rm = T), val)) %>% 
  ungroup %>% 
  spread(var, val) %>% 
  arrange(CTD) %>% 
  # filter(!CTD %in% 109) %>% 
  rename(
    `Int.diss` = internal,
    `Ext.diss` = external, 
    `Carapace.width` = avelen
  ) %>% 
  data.frame(stringsAsFactors = F, check.names = F) %>% 
  remove_rownames %>% 
  column_to_rownames('CTD')

datenv <- envdatdelt %>%
  filter(var %in% c('pH', 'pHdelt', 'Oxygen', 'Temperature', 'Chla')) %>% 
  filter(depth %in% 60) %>% 
  filter(CTD %in% row.names(datbio)) %>% 
  # complete(CTD, var) %>%
  group_by(var) %>% 
  mutate(val = ifelse(is.na(val), mean(val, na.rm = T), val)) %>% 
  ungroup %>% 
  spread(var, val) %>% 
  # filter(!CTD %in% 109) %>% 
  arrange(CTD) %>% 
  # mutate(
  #   Chla = ifelse(is.na(Chla), mean(Chla, na.rm = T), Chla)
  # ) %>% 
  data.frame(stringsAsFactors = F) %>% 
  remove_rownames %>% 
  column_to_rownames('CTD')

datbio <- datbio[!rownames(datbio) == 115, ]
datenv <- datenv[!rownames(datenv) == 115, ]

ord <- rda(datbio, datenv, scale = T)
ggord(ord, axes = c('1', '2'), vec_ext = 1, ptslab = T, parse = T, obslab = T, labcol = 'tomato1', repel = T, coord_fix = F, addsize = 3) + 
  theme_bw(base_family = 'serif') 
summary(ord)
```

## Figure 3

[download](figs/corplot.jpg)

```{r corplot, fig.height = 4.5, fig.width = 4.5}
datbio<- dissdat %>% 
  # filter(!CTD %in% c(109)) %>% 
  spread(prt, disval) %>% 
  mutate(
    external = `body part` + legs / 2
  ) %>% 
  select(CTD, internal, external)

lengdatsub <- lengdat %>% 
  filter(lenvar %in% 'CW')

abucrbs <- crbs %>% 
  dplyr::select(CTD, abundances)

datbio <- datbio %>% 
  left_join(lengdatsub, by = 'CTD') %>% 
  full_join(crbs, by = 'CTD') %>% 
  select(CTD, internal, external, avelen, abundances) %>% 
  rename(
    `Ext.diss` = external,
    `Int.diss` = internal, 
    `Abundances` = abundances,
    `Carapace.width` = avelen
  ) %>% 
  mutate(Abundances = log10(1 + Abundances))

pbase <- theme(
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(), 
  axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8), 
  axis.text.y = element_text(size = 8),
  legend.position = c(0.5, 1.12),
  legend.direction = 'horizontal',
  plot.margin = unit(c(4,4,0,0), "lines"),
  strip.background = element_blank(), 
  strip.text.y = element_text(angle = 0, hjust = 0, vjust = 0.5), 
  panel.background = element_rect(fill = 'black')
  ) 

outlab <- data.frame(
  y = c(2.5, 6.5), 
  lab = c('Environment', 'Biology')
)

##
# p1 

datenv <- envdatdelt %>% 
  filter(var %in% c('pH', 'pHdelt', 'Oxygen', 'Temperature','Chla')) %>% 
  filter(depth %in% 60) %>% 
  select(-depth) %>% 
  filter(CTD %in% datbio$CTD) %>% 
  complete(CTD, var) %>% 
  group_by(var) %>% 
  mutate(val = ifelse(is.na(val), mean(val, na.rm = T), val)) %>% 
  ungroup %>% 
  spread(var, val)

dat_cor <- datbio %>% 
  inner_join(datenv, by = 'CTD') %>% 
  dplyr::select(-CTD)

crs <- crossing(var1 = names(dat_cor), var2 = names(dat_cor)) %>% 
  filter(var1 != var2) %>% 
  rownames_to_column() %>% 
  group_by(rowname) %>% 
  nest %>% 
  mutate(
    crs = map(data, function(x){
      
      # variables
      vr1 <- dat_cor[[x$var1]]
      vr2 <- dat_cor[[x$var2]]
      
      # pearson
      pr_ts <- cor.test(vr1, vr2, method = 'pearson')
      pr_cr <- round(pr_ts$estimate, 2)
      pr_pv <- p_ast(pr_ts$p.value)
      pr <- paste(pr_cr, pr_pv)
    
      out <- data.frame(pr = pr, stringsAsFactors = F)
      return(out)
      
    })
  ) %>% 
  unnest %>% 
  select(-rowname)

levs <- names(dat_cor)
labs <- levs
prplo <- crs %>% 
  separate(pr, c('cor', 'sig'), sep = ' ') %>% 
  filter(var1 %in% levs & var2 %in% levs) %>%  
  mutate(
    cor = as.numeric(cor), 
    var1 = factor(var1, levels = rev(levs), labels = rev(labs)), 
    var2 = factor(var2, levels = rev(levs), labels = rev(labs)), 
    sig = gsub('ns', '', sig)
  )

p1 <- ggplot(prplo) + 
  geom_tile(aes(y = var1, x = var2, fill = cor), colour = 'black') + 
  geom_text(aes(y = var1, x = var2, label = sig)) +
  annotation_custom(grob = textGrob(label = outlab$lab[1], hjust = 0, gp = gpar(cex = 0.6)),
                    ymin = outlab$y[1], ymax = outlab$y[1], xmin = 9.75, xmax = 9.75) +
  annotation_custom(grob = textGrob(label = outlab$lab[2], hjust = 0, gp = gpar(cex = 0.6)),
                    ymin = outlab$y[2], ymax = outlab$y[2], xmin = 9.75, xmax = 9.75) +
  annotation_custom(grob = textGrob(label = outlab$lab[1], hjust = 0.5, gp = gpar(cex = 0.6)),
                    xmin = outlab$y[1], xmax = outlab$y[1], ymin = 9.75, ymax = 9.75) +
  annotation_custom(grob = textGrob(label = outlab$lab[2], hjust = 0.5, gp = gpar(cex = 0.6)),
                    xmin = outlab$y[2], xmax = outlab$y[2], ymin = 9.75, ymax = 9.75) +
  pbase +
  scale_y_discrete('', expand = c(0, 0), labels = parse(text = rev(labs))) + 
  scale_x_discrete('', expand = c(0, 0), labels = parse(text = rev(labs))) +
  scale_fill_gradient2('Correlation', low = muted("blue"), mid = "white", high = muted("green"), midpoint = 0, limits = c(-1, 1)) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0))) +
  geom_hline(yintercept = 5.5, size = 1.5) +
  geom_vline(xintercept = 5.5, size = 1.5) 


# Code to override clipping
gt1 <- ggplot_gtable(ggplot_build(p1))
gt1$layout$clip[gt1$layout$name == "panel"] <- "off"
grid.arrange(
  gt1
  # arrangeGrob(textGrob('60 m'), gt1, ncol = 1, heights = c(0.05, 1)), 
  # ncol = 2
)
```

