---
output: 
  bookdown::html_document2:
    code_folding: hide
---

```{r message = F, warning = F, results = 'hide',echo=F}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, fig.path = 'figs/', dev.args = list(family = 'serif'))

library(tidyverse)
library(patchwork)
library(ggrepel)
library(vegan)
library(ggord)
library(grid)
library(gridExtra)
library(scales)

prj <- 4326 # wgs84

source('R/funcs.R')

pbase <- theme_bw(base_size = 12, base_family = 'serif') + 
  theme(
    # axis.title = element_blank(), 
    strip.background = element_blank() 
  ) 

data(dissdat)
data(crbs)
data(lengdat)
data(envdatdelt)
data(shoreloc)

# get all values and only ph delt
envdatdelt <- envdatdelt %>% 
  gather('envtyp', 'envval', val, delt) %>% 
  unite('var', var, envtyp, sep = '') %>% 
  filter(grepl('val$|^pHdelt|^Calcitedelt$|^Temperaturedelt$|^Oxygendelt$', var)) %>% 
  mutate(var = gsub('\\val$', '', var)) %>% 
  rename(val = envval) %>% 
  mutate(
    val = ifelse(var %in% 'Chla', log10(val), val)
  )
```

# Figures and tables {.tabset}

## Table 1

Summary of environmental data at 60 m for sites that are onshore (less than 200 m depth) and those that are offshore (greater than 200 m depth).  
```{r}
totab <- envdatdelt %>% 
  mutate(
    val = ifelse(var %in% 'Chla', 10 ^ val, val) # back-transform chla for table
  ) %>% 
  filter(CTD %in% dissdat$CTD) %>% 
  filter(depth %in% 60) %>%
  filter(!grepl('delt$', var)) %>% 
  left_join(shoreloc, by = 'CTD') %>% 
  select(-depth) %>% 
  group_by(var, shoreloc) %>% 
  summarise(
    avev = mean(val, na.rm = T), 
    medv = median(val, na.rm = T), 
    minv = min(val, na.rm = T), 
    maxv = max(val, na.rm = T)
  ) %>% 
  ungroup %>% 
  gather('varv', 'valv', -var, -shoreloc) %>% 
  mutate(
    valv = ifelse(var %in% c('Oxygen', 'Temperature', 'pCO2'), round(valv, 1), round(valv, 2)),
    valv = as.character(valv)
  ) %>% 
  spread(varv, valv) %>% 
  arrange(desc(shoreloc), var) %>% 
  mutate(
    shoreloc = factor(shoreloc, levels = c('onshore', 'offshore'), labels = c('Onshore', 'Offshore')),
    shoreloc = as.character(shoreloc),
    shoreloc = ifelse(duplicated(shoreloc), '', shoreloc)
  ) %>% 
  dplyr::select(shoreloc, var, avev, medv, minv, maxv) %>% 
  rename(
    Location = shoreloc,
    Parameter = var,
    Average = avev,
    Median = medv,
    Minimum = minv,
    Maximum = maxv
  )

knitr::kable(totab)
```

## Figure 1

[download](figs/regplot-1.png)

```{r regplot, fig.height = 7, fig.width = 7, fig.cap = ''}

envplo <- envdatdelt %>% 
  filter(var %in% c('Calcitedelt', 'pCO2')) %>% 
  filter(depth %in% 60) %>% 
  filter(CTD %in% crbs$CTD) %>% 
  dplyr::select(CTD, var, val) %>% 
  spread(var, val)

displo <- dissdat %>% 
  spread(prt, disval) %>% 
  # filter(!CTD %in% 109) %>%
  mutate(
    external = (`body part` + legs) / 2
  ) %>% 
  # gather('var', 'val', internal, external) %>% 
  # mutate(val = scales::rescale(val)) %>% 
  # spread(var, val) %>% 
  select(CTD, internal, external)

lenplo <- lengdat %>% 
  filter(lenvar %in% 'CW') %>% 
  dplyr::select(CTD, avelen)

toplo <- displo %>% 
  left_join(lenplo, by = 'CTD') %>% 
  left_join(envplo, by = 'CTD') %>% 
  left_join(shoreloc, by = 'CTD')

p1 <- ggplot(toplo, aes(x = Calcitedelt, y = external, colour = shoreloc)) + 
  geom_point(size = 2.5, alpha = 0.8) + 
  pbase + 
  theme(
    legend.title = element_blank(), 
    legend.position = 'none'
    ) + 
  scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
  xlab(expression(paste(Delta, 'Calcite'[60]))) +
  ylab('Relative external dissolution') +
  # scale_y_continuous(limits = c(0, 1)) +
  geom_smooth(method = 'lm', se = F, linetype = 'dashed', colour = 'black') + 
  geom_text_repel(aes(label = CTD), size = 3, show.legend = F) + 
  guides(text) +
  ggtitle('(a)') 

p2 <- ggplot(toplo, aes(x = pCO2, y = internal, colour = shoreloc)) + 
  geom_point(size = 2.5, alpha = 0.8) + 
  pbase + 
  theme(
    legend.title = element_blank(), 
    legend.position = 'none'
    ) + 
  scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
  xlab(expression(paste('pCO2'[60]))) +
  ylab('Relative internal dissolution') +
  # scale_y_continuous(limits = c(0, 1)) +
  geom_smooth(method = 'lm', se = F, linetype = 'dashed', colour = 'black') + 
  geom_text_repel(aes(label = CTD), size = 3, show.legend = F) + 
  guides(text) +
  ggtitle('(b)') 

p3 <- ggplot(toplo, aes(x = internal,  y = external, colour = shoreloc)) + 
  geom_point(size = 2.5, alpha = 0.8) + 
  xlab('Relative internal dissolution') + 
  ylab('Relative external dissolution') + 
  geom_abline(slope = 1, intercept = 0) + 
  pbase + 
  theme(
    legend.title = element_blank(), 
    legend.position = 'none'
    ) + 
  scale_y_continuous(limits = c(0, 1)) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
  geom_smooth(method = 'lm', se = F, linetype = 'dashed', colour = 'black') + 
  geom_text_repel(aes(label = CTD), size = 3, show.legend = F) + 
  ggtitle('(c)') 


onshoredat <- toplo %>% 
  filter(shoreloc %in% 'onshore')
p4 <- ggplot(toplo, aes(x = external,  y = avelen, colour = shoreloc)) + 
  geom_point(size = 2.5, alpha = 0.8) +  
  xlab('Relative external dissolution') + 
  ylab('Carapace width (mm)') + 
  pbase + 
  theme(
    legend.title = element_blank(), 
    legend.position = 'top'
    ) + 
  # scale_y_continuous(limits = c(0, 1)) + 
  # scale_x_continuous(limits = c(0, 1)) +
  scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
  geom_smooth(method = 'lm', se = F, linetype = 'dashed', colour = 'black') + 
  geom_smooth(data = onshoredat, method = 'lm', se= F, linetype = 'solid', colour = 'aquamarine3',alpha = 0.7) +
  geom_text_repel(aes(label = CTD), size = 3, show.legend = F) + 
  ggtitle('(d)') 

pleg <- g_legend(p4)
p4 <- p4 + theme(legend.position = 'none')

wrap_elements(pleg) + (p1 + p2 + p3 + p4 + plot_layout(ncol = 2)) + plot_layout(ncol = 1, heights = c(0.05, 1))
```

Estimated linear relationships between different pH gradients and disslution. a) $\Delta Calcite_{60}$ and relative external dissolution (R2 = 0.87; p < 0.001).  b) Depth-integrated pH at 60m and relative internal dissolution (R2 = 0.41; p = 0.064). c) Comparison of the relative external and internal dissolution (R2 = 0.24; p = 0.18). d) Relative external dissolution and carapace width (R2 = 0.57; p = 0.08).  Dotted lines show the linear regression fit between all points.  The solid line in (c) is the 1:1 line and the green line in (d) is the regression fit only through the onshore points. See methods for explanation of the term relative dissolution. 

Panel a:
```{r}
lm(external ~ Calcitedelt, data = toplo) %>% summary
```

Panel b:
```{r}
lm(internal ~ pCO2, data = toplo) %>% summary
```

Panel c:
```{r}
lm(external ~ internal, data = toplo) %>% summary
```

Panel d:
```{r}
lm(avelen ~ external, data = onshoredat) %>% summary
```

### Internal dissolution and pH

```{r}
# dissolution predictions for internal, 10m model, onshore only

envplo <- envdatdelt %>% 
  filter(var %in% c('pHdelt', 'pH')) %>% 
  filter(depth %in% 60) %>% 
  filter(CTD %in% crbs$CTD) %>% 
  dplyr::select(CTD, var, val) %>% 
  spread(var, val)

displo <- dissdat %>% 
  spread(prt, disval) %>% 
  # filter(!CTD %in% 109) %>%
  mutate(
    external = (`body part` + legs) / 2
  ) %>% 
  # gather('var', 'val', internal, external) %>% 
  # mutate(val = scales::rescale(val)) %>% 
  # spread(var, val) %>% 
  select(CTD, internal, external)

lenplo <- lengdat %>% 
  filter(lenvar %in% 'CW') %>% 
  dplyr::select(CTD, avelen)

toplo <- displo %>% 
  left_join(lenplo, by = 'CTD') %>% 
  left_join(envplo, by = 'CTD') %>% 
  left_join(shoreloc, by = 'CTD') %>% 
  filter(shoreloc %in% 'onshore')

phmod <- lm(internal ~ pH, toplo)

df <- data.frame(
    pH = c(8.17, 8.043, 7.92, 7.82), 
    lab = c('pre-industrial', 'current', 'future45', 'future85')
  ) %>% 
  mutate(
    internal = predict(phmod, newdata = ., se.fit = T)$fit,
    sefit = predict(phmod, newdata = ., se.fit = T)$se.fit, 
    perchg = (internal - subset(internal, lab == 'current')) / subset(internal, lab == 'current')
  )
df
```

### External dissolution and delta pH

Baseline pHdelt is mean of phDelt observations for 60m.  Pre-industrial is the baseline phDelt - 2 \* 0.02 (estimated decadal change for two decades prior).   Post-industrial is the baseline phDelt + 2 \* 0.02 (estimated decadal change for 2 decades post)
```{r}
# dissolution predictions for external, deltph model, onshore only, 60 m

envplo <- envdatdelt %>% 
  filter(var %in% c('pHdelt', 'pH')) %>% 
  filter(depth %in% 60) %>% 
  # filter(CTD %in% crbs$CTD) %>% 
  dplyr::select(CTD, var, val) %>% 
  spread(var, val)

displo <- dissdat %>% 
  spread(prt, disval) %>% 
  # filter(!CTD %in% 109) %>%
  mutate(
    external = (`body part` + legs) / 2
  ) %>% 
  select(CTD, internal, external)

lenplo <- lengdat %>% 
  filter(lenvar %in% 'CW') %>% 
  dplyr::select(CTD, avelen)

toplo <- displo %>% 
  left_join(lenplo, by = 'CTD') %>% 
  left_join(envplo, by = 'CTD') %>% 
  left_join(shoreloc, by = 'CTD') %>% 
  filter(shoreloc %in% 'onshore')

phdeltmod <- lm(external ~ pHdelt, toplo)

decchn <- 0.02
bsedlt <- mean(envplo$pHdelt)
df <- data.frame(
    pHdelt = c(bsedlt - 2 * 0.02, bsedlt, bsedlt + 2 * 0.02), 
    lab = c('pre-industrial', 'current', 'future')
  ) %>% 
  mutate(
    external = predict(phdeltmod, newdata = ., se.fit = T)$fit,
    sefit = predict(phdeltmod, newdata = ., se.fit = T)$se.fit, 
    perchg = (external - subset(external, lab == 'current')) / subset(external, lab == 'current')
  )
df
```

### Delta calcite vs deltapH

[download](figs/calcvph-1.png)

```{r calcvph, fig.height = 4, fig.width = 3.75}
toplo <- envdatdelt %>% 
  filter(var %in% c('pHdelt', 'Calcitedelt')) %>% 
  filter(depth %in% 60) %>% 
  filter(CTD %in% displo$CTD) %>%
  dplyr::select(CTD, var, val) %>% 
  spread(var, val) %>% 
  left_join(shoreloc, by = 'CTD') 
  
ggplot(toplo, aes(x = pHdelt, y = Calcitedelt, colour = shoreloc)) +
  geom_point(size = 2.5, alpha = 0.8) + 
  xlab(expression(paste(Delta, 'pH'[60]))) +
  ylab(expression(paste(Delta, 'Calcite'[60]))) +
  pbase + 
  theme(
    legend.title = element_blank(), 
    legend.position = 'top'
  ) + 
  scale_colour_manual(values = c('deepskyblue3', 'aquamarine3')) +
  geom_smooth(method = 'lm', se = F, linetype = 'dashed', colour = 'black') +
  geom_text_repel(aes(label = CTD), size = 3, show.legend = F)
```

```{r}
summary(lm(Calcitedelt ~ pHdelt, toplo))
```

## Figure 2

[download](figs/rdaplot-1.png)

```{r rdaplot, fig.height = 4, fig.width = 4}
datbio <- dissdat %>% 
  # filter(!CTD %in% c(109)) %>%
  spread(prt, disval) %>% 
  mutate(
    external = `body part` + legs
  ) %>% 
  select(CTD, internal, external)

lengdatsub <- lengdat %>% 
  filter(lenvar %in% 'CW')

datbio <- datbio %>% 
  left_join(lengdatsub, by = 'CTD') %>% 
  select(CTD, internal, external, avelen) %>% 
  gather('var', 'val', internal, external, avelen) %>% 
  group_by(var) %>% 
  mutate(val = ifelse(is.na(val), mean(val, na.rm = T), val)) %>% 
  ungroup %>% 
  spread(var, val) %>% 
  arrange(CTD) %>% 
  # filter(!CTD %in% 109) %>% 
  rename(
    `Int.diss` = internal,
    `Ext.diss` = external, 
    `Width` = avelen
  ) %>% 
  data.frame(stringsAsFactors = F, check.names = F) %>% 
  remove_rownames %>% 
  column_to_rownames('CTD')

datenv <- envdatdelt %>%
  filter(var %in% c('pCO2', 'Temperature', 'Calcitedelt', 'pH', 'Oxygen')) %>% 
  filter(depth %in% 60) %>% 
  filter(CTD %in% row.names(datbio)) %>% 
  # complete(CTD, var) %>%
  group_by(var) %>% 
  mutate(val = ifelse(is.na(val), mean(val, na.rm = T), val)) %>% 
  ungroup %>% 
  spread(var, val) %>% 
  # filter(!CTD %in% 109) %>% 
  arrange(CTD) %>% 
  # mutate(
  #   Chla = ifelse(is.na(Chla), mean(Chla, na.rm = T), Chla)
  # ) %>% 
  data.frame(stringsAsFactors = F) %>% 
  remove_rownames %>% 
  column_to_rownames('CTD') %>% 
  dplyr::select(-depth)

datbio <- datbio[!rownames(datbio) == 115, ]
datenv <- datenv[!rownames(datenv) == 115, ]

ord <- rda(datbio, datenv, scale = T)
ggord(ord, axes = c('1', '2'), vec_ext = 1, ptslab = T, parse = T, obslab = T, labcol = 'tomato1', repel = T, coord_fix = F, addsize = 3) + 
  theme_bw(base_family = 'serif') 
summary(ord)
```

```{r eval = F}
datbio <- datbio %>% 
  rownames_to_column('CTD')
tomod <- datenv %>% 
  vegan::decostand(method = 'standardize') %>%
  rownames_to_column('CTD') %>% 
  full_join(datbio, by = 'CTD')

# oxygen is collinear with pCO2, do not include
mod1 <- lm(Int.diss ~ (pCO2 + Temperature + Oxygen), data = tomod)
summary(mod1)
summary(step(mod1, direction = 'backward'))

mod2 <- lm(Ext.diss ~ (Calcitedelt + Oxygendelt + Temperaturedelt), data = tomod)
summary(mod2)
summary(step(mod2, direction ='backward'))

mod3 <- lm(Carapace.width ~ (pCO2 + Temperature + Chla + Calcitedelt + Oxygendelt + Temperaturedelt), data = tomod)
summary(mod3)
summary(step(mod3, direction = 'backward'))
```

## Figure 3

[download](figs/corplot-1.png)

```{r corplot, fig.height = 4.5, fig.width = 4.5}
datbio<- dissdat %>% 
  # filter(!CTD %in% c(109)) %>% 
  spread(prt, disval) %>% 
  mutate(
    external = `body part` + legs / 2
  ) %>% 
  select(CTD, internal, external)

lengdatsub <- lengdat %>% 
  filter(lenvar %in% 'CW')

abucrbs <- crbs %>% 
  dplyr::select(CTD, abundances)

datbio <- datbio %>% 
  full_join(abucrbs, by = 'CTD') %>% 
  left_join(lengdatsub, by = 'CTD') %>% 
  select(CTD, internal, external, avelen, abundances) %>% 
  rename(
    `Ext.diss` = external,
    `Int.diss` = internal, 
    `Abundances` = abundances,
    `Carapace.width` = avelen
  ) %>% 
  mutate(Abundances = log10(1 + Abundances))

pbase <- theme(
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(), 
  axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8), 
  axis.text.y = element_text(size = 8),
  legend.position = c(0.5, 1.12),
  legend.direction = 'horizontal',
  plot.margin = unit(c(4,4,0,0), "lines"),
  strip.background = element_blank(), 
  strip.text.y = element_text(angle = 0, hjust = 0, vjust = 0.5), 
  panel.background = element_rect(fill = 'black')
  ) 

outlab <- data.frame(
  y = c(3, 7.5), 
  lab = c('Environment', 'Biology')
)

##
# p1 

# levels, labels
levs <- c('Int.diss', 'Ext.diss', 'Carapace.width', 'Abundances', 'Calcitedelt', 'pCO2', 'Temperature', 'Oxygen', 'Chla')
labs <- c('Int.~diss', 'Ext.~diss', 'Carapace~width', 'Abundances', 'Delta~Calcite', 'pCO[2]', 'Temp', 'O[2]', 'Chla')

datenv <- envdatdelt %>% 
  filter(var %in% levs) %>% 
  filter(depth %in% 60) %>% 
  select(-depth) %>% 
  filter(CTD %in% datbio$CTD) %>% 
  complete(CTD, var) %>% 
  group_by(var) %>% 
  mutate(val = ifelse(is.na(val), mean(val, na.rm = T), val)) %>% 
  ungroup %>% 
  spread(var, val)

dat_cor <- datbio %>% 
  inner_join(datenv, by = 'CTD') %>% 
  dplyr::select(-CTD)

crs <- crossing(var1 = names(dat_cor), var2 = names(dat_cor)) %>% 
  filter(var1 != var2) %>% 
  rownames_to_column() %>% 
  group_by(rowname) %>% 
  nest %>% 
  mutate(
    crs = map(data, function(x){
      
      # variables
      vr1 <- dat_cor[[x$var1]]
      vr2 <- dat_cor[[x$var2]]
      
      # pearson
      pr_ts <- cor.test(vr1, vr2, method = 'pearson')
      pr_cr <- round(pr_ts$estimate, 2)
      pr_pv <- p_ast(pr_ts$p.value)
      pr <- paste(pr_cr, pr_pv)
    
      out <- data.frame(pr = pr, stringsAsFactors = F)
      return(out)
      
    })
  ) %>% 
  unnest %>% 
  select(-rowname)

prplo <- crs %>% 
  separate(pr, c('cor', 'sig'), sep = ' ') %>% 
  filter(var1 %in% levs & var2 %in% levs) %>%  
  mutate(
    cor = as.numeric(cor), 
    var1 = factor(var1, levels = rev(levs), labels = rev(labs)), 
    var2 = factor(var2, levels = rev(levs), labels = rev(labs)), 
    sig = gsub('ns', '', sig)
  )

p1 <- ggplot(prplo) + 
  geom_tile(aes(y = var1, x = var2, fill = cor), colour = 'black') + 
  geom_text(aes(y = var1, x = var2, label = sig)) +
  annotation_custom(grob = textGrob(label = outlab$lab[1], hjust = 0, gp = gpar(cex = 0.6)),
                    ymin = outlab$y[1], ymax = outlab$y[1], xmin = 9.75, xmax = 9.75) +
  annotation_custom(grob = textGrob(label = outlab$lab[2], hjust = 0, gp = gpar(cex = 0.6)),
                    ymin = outlab$y[2], ymax = outlab$y[2], xmin = 9.75, xmax = 9.75) +
  annotation_custom(grob = textGrob(label = outlab$lab[1], hjust = 0.5, gp = gpar(cex = 0.6)),
                    xmin = outlab$y[1], xmax = outlab$y[1], ymin = 9.75, ymax = 9.75) +
  annotation_custom(grob = textGrob(label = outlab$lab[2], hjust = 0.5, gp = gpar(cex = 0.6)),
                    xmin = outlab$y[2], xmax = outlab$y[2], ymin = 9.75, ymax = 9.75) +
  pbase +
  scale_y_discrete('', expand = c(0, 0), labels = parse(text = rev(labs))) + 
  scale_x_discrete('', expand = c(0, 0), labels = parse(text = rev(labs))) +
  scale_fill_gradient2('Correlation', low = muted("blue"), mid = "white", high = muted("green"), midpoint = 0, limits = c(-1, 1)) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 6, angle = 0))) +
  geom_hline(yintercept = 5.5, size = 1.5) +
  geom_vline(xintercept = 5.5, size = 1.5) 


# Code to override clipping
gt1 <- ggplot_gtable(ggplot_build(p1))
gt1$layout$clip[gt1$layout$name == "panel"] <- "off"
grid.arrange(
  gt1
  # arrangeGrob(textGrob('60 m'), gt1, ncol = 1, heights = c(0.05, 1)), 
  # ncol = 2
)
```

